---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(naturalstattrick)
```

# naturalstattrick

<!-- badges: start -->
[![R-CMD-check](https://github.com/pbulsink/naturalstattrick/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/pbulsink/naturalstattrick/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/pbulsink/naturalstattrick/graph/badge.svg?token=1eceI2f2pK)](https://codecov.io/gh/pbulsink/naturalstattrick)
<!-- badges: end -->

The goal of naturalstattrick is to provide a convenient and basic interface to game-level Natural Stat Trick data. 

## Installation

You can install the development version of naturalstattrick from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pbulsink/naturalstattrick")
```

## Usage 

Get a game's results by calling:
```{r full_report}
get_game_report(season = 20222023, game_id = 20041)
```

The `game_id` parameter is of the NHL Game ID style and season a 8 digit number (i.e. 20222023 for the 2022-2023 season).

Alternatively rearrange the output by calling:
```{r nst_report}
nst_report(20222023, 20041)
```

Note that the abbreviations are all explained on the Natural Stat Trick website at https://www.naturalstattrick.com/glossary.php?teams.
